Approximation as Differentiation

### 2025-07-10 main/language.tex
Get a bit clear on how we get the model of Sigma.

Given a model $M$ of $\Sigma$ in $\Fam(\LatGal)$, the category $\Fam(\MeetSLat \times \JoinSLat^\op)$ can
implement $\Sem$. It is bicartesian closed by \corref{mslat-jslat-bcc}, and can model $\List(X)$ as an
infinite coproduct (\secref{models-of-total-gps:coproducts-and-products}). A model $H(M)$ of $\Sigma$ can be
obtained via the embedding $\HoEmbed: \Fam(\LatGal) \to \Fam(\MeetSLat \times \JoinSLat^\op)$ given in
\propref{ho-embedding}, because .... Finally $\LatGal$ has a lifting monad which is preserved by the 2-functor
$\Fam: \Cat \to \Cat$ (\secref{first-order:lifting}). The correctness of this interpretation is considered in
the next section.

>>>>

Given a model $M$ of $\Sigma$ in $\Fam(\LatGal)$, the category $\Fam(\MeetSLat \times \JoinSLat^\op)$ can
implement $\Sem$. It is bicartesian closed by \corref{mslat-jslat-bcc}, and can model $\List(X)$ as an
infinite coproduct (\secref{models-of-total-gps:coproducts-and-products}). A model $H(M)$ of $\Sigma$ can be
obtained via the embedding $\HoEmbed: \Fam(\LatGal) \to \Fam(\MeetSLat \times \JoinSLat^\op)$ given in
\propref{ho-embedding}, because the functor $\Fam: \Cat \to \Cat$ preserves finite products and so does the
embedding. Finally $\LatGal$ has a lifting monad which is also preserved by $\Fam$
(\secref{first-order:lifting}). The correctness of this interpretation is considered in the next section.
